Arbitrary Precision and Arbitrary $n$-Grams

### 2011-03-01 paper/paper.Rnw
further paper changes
paper stuff

	%\\

@@

		Our hypothesis was that the arbitrary precision math would reveal a
		small amount of error in computing the perplexity logarithmically.  Our
		results seem to indicate that any such error is very small (differing
		only in the last digit in measuring the perplexity of whole corpora),
		but that arbitrary-precision mathematics is much slower than floating
		point mathematics with logs when finding the product of many numbers.
		See \ref{runtimes}:

		\begin{table}
		\caption{Running times with arbitrary and floating-point precision in
		seconds.  Average of 10 trials, trained on the Shakespeare training
		corpus, perplexity calculated for Shakespeare training corpus}
		\label{runtimes}
		\begin{tabular}{l | r r}
			Operation & Arbitrary Precision & Logarithmic \\
			\hline
			Trigram tallying & 136.936949968 & 137.023640156\\
			Probability computation & 63.5648961067 & 60.1038038731 \\
			Perplexity computation & \textbf{990.322752953} & 65.2168021202 \\
		\end{tabular}
		\end{table}

>>>>

@@

		Our hypothesis was that the arbitrary precision math would reveal a
		small amount of error in computing the perplexity logarithmically.  Our
		results seem to indicate that any such error is very small (differing
		only in the last digit in measuring the perplexity of whole corpora),
		but that arbitrary-precision mathematics is much slower than floating
		point mathematics with logs when finding the product of many numbers.
		See table \ref{runtimes}.  This suggests that the logarithmic
		computation is indeed an accurate way to compute perplexity,
		particularly in light of the more than \osn{10}-fold speed improvements
		it results in.

		\begin{table}[h]
		\begin{tabular}{l | r r}
			Operation & Arbitrary Precision & Logarithmic \\
			\hline
			Trigram tallying & 136.936949968 & 137.023640156\\
			Probability computation & 63.5648961067 & 60.1038038731 \\
			Perplexity computation & \textbf{990.322752953} & 65.2168021202 \\
		\end{tabular}
		\caption{Running times with arbitrary and floating-point precision in
		seconds.  Average of \osn{10} trials, trained on the Shakespeare
		training corpus, perplexity calculated for Shakespeare training corpus}
		\label{runtimes}
		\end{table}
